Argennon: A Scalable Smart Contract Platform

### 2021-07-13 tex/sections/avm.tex
Add the virtual signature concept
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, first we need to make sure that the sender has authorized this operation. The
Argennon virtual machine has no built-in mechanism for authorizing operations, but it provides a rich set of
cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
passing cryptographic signatures as parameters to methods, a programmer can implement the required logic
for authorizing any operation.

@@

In addition to signatures, a method can verify its invoker by using \texttt{get\_parent} instruction. This
instruction gets the \texttt{applicationID} of the smart contract that is one level deeper than the current
smart contract in the call stack or if there is none, the smart contract that created the current call stack.
In other words, it returns the \texttt{applicationID} of the smart contract that has invoked or spawned
the current smart contract.

>>>>

In blockchain applications, we usually need to authorize certain operations. For example, for sending an asset
from a user to another user, first we need to make sure that the sender has authorized this operation. The
Argennon virtual machine has no built-in mechanism for authorizing operations, but it provides a rich set of
cryptographic instructions for validating signatures and cryptographic entities. By using these instructions and
passing cryptographic signatures as parameters to methods, a programmer, having user's public keys, can implement
the required logic for authorizing any operation.

\note{Authorization by explicit signatures eliminates the need for approval methods or call back patterns.}

In addition to cryptographic signatures, the Argennon Virtual Machine provides instructions that enable
smart contracts to issue \emph{virtual signatures}. A smart contract can virtually sign a message for a target
smart contract by \texttt{v\_sign} instruction. When a smart contract
virtually signs a message for a target, that message is stored in the internal memory of the AVM, associated with
its signer and the target. The application that is the target of the signature can verify the message
by \texttt{v\_verify} instruction. After verifying the signature, it will be removed from the AVM's internal memory
to make sure a signature will not be used multiple times. The virtual signatures stored in the AVM's internal memory
last for one execution session.

@@

### 2021-07-13 tex/sections/elements.tex
Add the virtual signature concept
Signed-off-by: aybehrouz <behrouz_ayati@yahoo.com>

An application identifier can
be considered as the address of an application and has the following standard symbolic representation:
\begin{verbatim}
<application-id> ::= "["<hex-prefix-code>"]"
<hex-prefix-code> ::= "0x"<hex-num>"."<hex-prefix-code> | "0x"<hex-num>
\end{verbatim}
where \texttt{<hex-num>} is a hexadecimal number between $0$ and $255$, using lower case
letters \texttt{[a-f]} for showing digits greater than $9$.

For example \texttt{[0x24.0xff.0xda]}, \texttt{[0x0]} and \texttt{[0x3.0xa0.0x0.0x0]}, are valid application addresses.

@@

The root application or the root smart contract, with \texttt{applicationID=[0x0]}, is a privileged smart contract
responsible for installation/uninstallation of other smart contracts. The Argennon root smart contract
performs three main operations:

@@

The ARG application or the ARG smart contract,
with \texttt{applicationID=[0x1]}, controls the ARG token, the main
currency of the Argennon blockchain. This smart contract also manages a database of public keys and
handles signature verification.

@@

Argennon accounts are entities defined inside the ARG smart contract.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix
tree. (See Section~\ref{sec:identifiers}) An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= "["<decimal-prefix-code>"]"
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

For example \texttt{[21.255.37]}, \texttt{[0]} and \texttt{[1.0.0.0.0]}, are valid standard symbolic representations
of account addresses.

@@

\begin{itemize}
    \item Maximum internal execution cost
    \item Maximum external execution cost
    \item A list of heap/code-area locations for reading
    \item A list of heap locations for writing
    \item A list of heap chunks it will deallocate
    \item A list of methods it will delete (if any)
    \item Number and size of heap chunks it will allocate
    \item Number and size of method bytecodes it will allocate (if any)
\end{itemize}

@@

>>>>

An application identifier can
be considered as the address of an application and has the following standard symbolic representation:
\begin{verbatim}
<application-id> ::= <decimal-prefix-code>
<decimal-prefix-code> ::= <dec-num>"."<decimal-prefix-code> | <dec-num>
\end{verbatim}
where \texttt{<dec-num>} is a normal decimal number between $0$ and $255$.

For example \texttt{21.255.37}, \texttt{0} and \texttt{1.0.0.0.0}, are valid application addresses.

@@

The root application or the root smart contract, with \texttt{applicationID = 0}, is a privileged smart contract
responsible for installation/uninstallation of other smart contracts. The Argennon root smart contract
performs three main operations:

@@

The ARG application or the ARG smart contract,
with \texttt{applicationID = 1}, controls the ARG token, the main
currency of the Argennon blockchain. This smart contract also manages a database of public keys and
handles signature verification.

@@

Argennon accounts are entities defined inside the ARG smart contract.
Every Argennon account is uniquely identified by a prefix code generated using \emph{accounts} prefix
tree. (See Section~\ref{sec:identifiers}) An account
identifier can be considered as the address of an account and has the following standard symbolic representation:
\begin{verbatim}
<account-id> ::= <hex-prefix-code>
<hex-prefix-code> ::= "0x"<hex-num>"."<hex-prefix-code> | "0x"<hex-num>
\end{verbatim}
where \texttt{<hex-num>} is a hexadecimal number between $0$ and $255$, using lower case
letters \texttt{[a-f]} for showing digits greater than $9$.

For example \texttt{0x24.0xff.0xda}, \texttt{0x0} and \texttt{0x3.0xa0.0x0.0x0}, are valid standard symbolic
representations of account addresses.

@@

\begin{itemize}
    \item Maximum internal execution cost
    \item Maximum external execution cost
    \item A list of heap/code-area locations for reading
    \item A list of heap locations for writing
    \item A list of heap chunks it will deallocate (if any)
    \item A list of methods it will delete (if any)
    \item Number and size of heap chunks it will allocate (if any)
    \item Number and size of method bytecodes it will allocate (if any)
\end{itemize}

@@

\begin{lstlisting}[language=python, frame=TB, float, title=An Argennon transaction in YAML format,label={lst:txn-example}]
---
fee: |
    PUT /balances/0x73.0xa2?to=fee&amount=0.26&sig=5b73CbmwQNRC7fWUY15 HTTP/1.1
call: |
    POST httpb://bac.argennon.net/54.189.21/proposals HTTP/1.1
    Content-Type: application/json; charset=utf-8
    Content-Length: 69

    {
        "name": "Grant Proposal",
        "recipient": "0x24.0x8f.0x29.0xa1",
        "amount": 25000,
        "sig"= "2a36Gtrw249wQCD70nWY49d"
    }
caps:
    internal: 2500000 # maximum number of AVM execution clocks
    external: 1000000
    read: [(2654,3),(15642,0),(15642,1),(15642,3)]
    write: [(15642,0),(20154,0),(20154,1)]
\end{lstlisting}
